\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

% * Briefly motivate problem domain, why is it an important domain?
% * What problem does the thesis solve?
% * What is the main contribution? -> The abstract should convince a reader to read the thesis, not necessary to explain anything, just provide an incentive to read
% * Keep the abstract short! A half page is enough.




% The increasing complexity and interconnectivity of modern networks necessitate robust security measures to protect against evolving threats.
This thesis analyzes the security of the SCION, a next-generation Internet architecture designed for high availability, scalability, and security, with a specific focus on Anapaya's proprietary SCION solutions.
The primary objectives are to investigate the security of the operation devices deployed at the Cyber-Defence Campus and evaluate the actual SCION protocol in use.
Furthermore, the interaction between the SCION network and the traditional Internet is analyzed through the execution of a real-world denial-of-service attack.

Our methodology combines automated tools and manual investigations to conduct a comprehensive security audit.
The findings reveal several critical vulnerabilities, including the lack of source authentication in the SCION protocol, insecure SSH and system configurations, and several critical weaknesses in Anapaya's SCION management system.
As a result, we were able to remotely render the devices inoperable in a matter of seconds, or silently gain control over them.

This thesis provides a significant contribution to the field by bridging the gap between past research, which focused on the security of open-source SCION, and the currently deployed SCION variant provided by Anapaya.
It underscores the importance of secure SCION deployments and the necessity of regular security assessments and updates to ensure that SCION remains robust in the face of evolving threats.